### 2024-05-25 chapters/glossary.tex
feat(metadata): update section
feat(sections): update processing-metadata section (#15)
* feat(metadata): update section

* feat(metadata): add section introduction

* Update color boxea

* feat(main.sty): add subsection custom style

* feat(main): remove duplicated import

* feat(bib): add OAI-PMH ref

* feat(metadata): add OAI-PMH subsection

* feat(metadata): add control de flux section

* feat(metadata): add implementation section

* Use correct double quotes
Update processing-log

>>>>

\newglossaryentry{DSpace}{
    name            = DSpace,
    description     = {TODO}
}

\newglossaryentry{DIM}{
    name            = DIM,
    description     = {DSpace Intermediate Metadata}
}

\newglossaryentry{TCP}{
    name            = TCP,
    description     = {Transmission Control Protocol}
}

\newglossaryentry{HTTP}{
    name            = HTTP,
    description     = {Hypertext Transfer Protocol}
}

\newglossaryentry{IP}{
    name            = IP,
    description     = {Internet Protocol}
}

\newglossaryentry{ISO}{
    name            = ISO,
    description     = {Internacional Organization for Standardization}
}

\newglossaryentry{POSIX}{
    name            = POSIX,
    description     = {Portable Operating System Interface X}
}

\newglossaryentry{NAT}{
    name            = NAT,
    description     = {Network Address Translation}
}

\newglossaryentry{handle}{
    name            = handle,
    description     = {TODO}
}

\newglossaryentry{CSS}{
    name            = CSS,
    description     = {Cascading Style Sheets}
}
